Time Series Bootstrapping For Solar Current

### 2021-12-08 deliverables/presentation.Rmd
Simplified preprocessing slides

# Preprocessing: Astronomical Adjustment

INSERT FIG 1 FROM PAPER HERE
- Astronomical adjustments performed on DNI to find *effective* solar irradiance
- Used: Latitude, longitude, time zone, tilt of the earth 
- $I_{eff} \propto I_{sun}cos(\Theta)$

# Preprocessing: Power processor

- This gives a procedure for translating effective irradiance to
current, given an operating voltage
- Uses:
  - Effective irradiance
  - Operating voltage
  - Properties of solar panel materials
  - Solar panel layout

# Preprocessing: Photovoltaic (PV) Module

- Power processing units are attached to PV modules to optimize power output for a given current input.
- Maximizes power $P=IV$ over voltage
- Here $I$ is a function of $V$
- Result: Optimal current

# Results

>>>>

# Preprocessing

1. Astronomical adjustment: GHI $\rightarrow$ effective irradiance
1. Power processor: Effective irradiance + voltage $\rightarrow$ current 
1. PV Module: Effective irradiance $\rightarrow$ current

# Postprocessed data
